### 2020-06-01 paper.tex
Add Paper Title
Add Keywords
Make Simulated Annealing Algorithm More Generic

\title{Paper Title\\}

@@

Insert keywords here

@@

\begin{algorithm}[H]
    \caption{Simulated Annealing}
    \begin{algorithmic}[1]
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \Require Circuit $C_{o}$
    \Ensure  Optimized placement configuration $\Phi$
       \State Generate an initial random cells placement $P$
     \State Set $\alpha = 0.995$
     \State Set temperature $T = 2 * number\; of\; cells\; of\; C_{o}$
     \State Set optimized circuit configuration $\Phi = P$
     \While{$T > 1$}
       \State $P^{'} = $ randomly generated cells placement
       \State $\Delta C = wirelength(P^{'}) - wirelength(P)$
       \If{$\Delta C < 0$}
           \State $P = P^{'}$
           \If{$wirelength(P) < wirelength(\Phi)$}
               \State $\Phi = P$
           \EndIf
       \ElsIf{$rand(0,1) < e^{-\Delta C/T}$}
           \State $P = P^{'}$
       \EndIf
       \State $T = T * \alpha$
     \EndWhile
    \State \textbf{return} $\Phi$
    \end{algorithmic} 
    \end{algorithm}

>>>>

\title{Improving Placement in VLSI Design Process via Hybridization of Simulated Annealing and Genetic Algorithms \\}

@@

Very-large-scale integration (VLSI), Standard cell placement, Computer-aided design (CAD), Simulated annealing, Genetic algorithms, Integrated circuits (ICs).

@@

\begin{algorithm}[H]
    \caption{Simulated Annealing}
    \begin{algorithmic}[1]
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \Ensure  Optimized solution $S$
       \State Create an initial solution $x$
     \State Set $\alpha \in (0,1)$, temperature $T$
     \State Set $S = x$
     \While{Stopping criterion is NOT satisfied}
       \State $x^{'} = $ a neighbouring solution
       \State Calculate $C(x^{'})$
       \State Calculate $\Delta C = C(x^{'}) - C(x)$
       \If{$\Delta C < 0$}
           \State $x = x^{'}$
           \If{$C(x) < C(S)$}
               \State $S = x$
           \EndIf
       \ElsIf{$rand(0,1) < e^{-\Delta C/T}$}
           \State $x = x^{'}$
       \EndIf
       \State $T = T * \alpha$
     \EndWhile
    \State \textbf{return} $S$
    \end{algorithmic} 
\end{algorithm}
